\LARGE \bf ``Those who can't do, teach'': a Teachable Robotic Agent for Children Learning Handwriting

### 2014-09-09 main.tex
Minor fixes

\subsection{Outcomes of Preliminary Studies}% * <deanna.m.hood@gmail.com> 2014-09-05T08:43:38.105Z:
%
% I guess this is what we call the non-experiments.. Are the dates important?
%

@@

    \item \textbf{All children believed that the robot was learning, and that
        they were the ones teaching it.} This was concluded from their responses
        when the children were asked directly. This is in contrast to a prior
        feasibility study for a version of the interaction which only allowed
        for touch-based feedback, not user demonstrations, in which three of the
        seven adult participants did not feel that it was their input which
        helped the robot improve.% * <deanna.m.hood@gmail.com>
        2014-09-05T09:46:49.117Z:
    %
    % probably can't just casually mention this study without going into more detail...
    %

@@

In terms of the interaction experience, the current experimental setting, while
technically autonomous, can not robustly recover from situations outside of the
nominal protocol (presented in section~\ref{sec4}), and consequently still requires the
presence of an experimenter. The interaction state machine would require to be
extended in non-trivial ways to allow for long, fully autonomous, interactions
with children.

>>>>

\subsection{Outcomes of Preliminary Studies}% * <deanna.m.hood@gmail.com> 2014-09-05T08:43:38.105Z:
%
% I guess this is what we call the non-experiments.. Are the dates important?
%
% ^ <deanna.m.hood@gmail.com> 2014-09-09T09:11:57.672Z.

@@

    \item \textbf{All children believed that the robot was learning, and that
        they were the ones teaching it.} This was concluded from their responses
        when the children were asked directly. This is in contrast to a prior
        feasibility study for a version of the interaction which only allowed
        for touch-based feedback, not user demonstrations, in which three of the
        seven adult participants did not feel that it was their input which
        helped the robot improve.
        % * <deanna.m.hood@gmail.com> 2014-09-05T09:46:49.117Z:
    %
    % probably can't just casually mention this study without going into more detail...
    %

@@

In terms of the interaction experience, the current experimental setting, while
technically autonomous, can not robustly recover from situations outside of the
nominal protocol (presented in Section~\ref{sec4}), and consequently still requires the
presence of an experimenter. The interaction state machine would require to be
extended in non-trivial ways to allow for long, fully autonomous, interactions
with children.
